Distribution-oblivious Programming with Dish

### 2019-10-02 pldi/draft.tex
Abstract placeholder

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
  Distributed systems offer notable benefits over centralized systems.
  Reaping these benefits, however, requires developers to develop and deploy
  software in a manner that makes distribution explicit---a process
  that is quite different from how they compose software for centralized
  systems.
% 
  \emph{Light-touch distribution} is a new approach for scaling out distribution-oblivious shell scripts.
  It leverages the fact that 
% introduced as a drop-in replacement of a language runtime's module system, 
  Our \sys prototype shows substantial speedups over 
  as well as the ability to operate on large input sizes, all without
  any developer input.
\end{abstract}

>>>>

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
  \nv{placeholder}
  Distributed systems offer notable benefits over centralized ones.
  Reaping these benefits, however, requires programming in a way that makes distribution explicit---\eg via new programming languages, distributed framework interfaces, or distribution annotations.
% 
%   \emph{Distribution-oblivious programming} is a new approach for..?
  This paper presents \sys, a shell variant that automatically and correctly scales out distribution-oblivious shell pipelines. %  with regards to the sequential program.
  % leveraging the insight that such programs already express stream computations, with their stages falling under a few, known distributability classes.
  \sys's insight is that shell pipelines already express stream computations that can automatically distributed.
  To achieve this, \sys
% a series of techniques for automatically 
decomposes primitives into distributability classes,
identifies high-distributability stages,
applies rewriting rules for largest possible subprograms,
and orchestrates the distributed program.
Its runtime component provides orchestration and planning support during the execution of the program.
% 
% Key challenges include 
% surprisingly expressive, 
% maximally distributable subprograms
% 
Experiments for complex pipelines show substantial speedups and the ability to operate on large input datasets, all without any developer input.
\end{abstract}
